---
title: "HLM on Craigslist Discourse"
output: html_notebook
---

#Overview
This is the main analysis file. It takes a dataset of craigslist texts with two 40-topic STM fits, and runs analysis to assess the association with neighborhood racial proportions.

```{r load libraries}
library(tidyverse)
library(lme4)
library(forcats)
source('hlm_support.R')
```

#Load Data and transform
```{r}
data <- read_csv('data/hlm_cl.csv')
dataT <- data

#log transformed topic proportions
dataT$Topic7 <- log(data$Topic7) #trying not to mess with anything in hlm_support right now, yes I know this is a hack
dataT$Topic18 <- log(data$Topic18)
dataT$Topic20 <- log(data$Topic20)
dataT$Topic25 <- log(data$Topic25)
dataT$Topic34 <- log(data$Topic34)

#log1p transformed racial proportions
dataT$white_proportion <- log1p(data$white_proportion)
dataT$black_proportion <- log1p(data$black_proportion)
dataT$asian_proportion <- log1p(data$asian_proportion)
dataT$latinx_proportion <- log1p(data$latinx_proportion)

``` 

```{r}
#coef_sum_bi_glm <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), model_type = 'glm', family = 'binomial')
#plot_coef_sum(coef_sum_bi_glm)
coef_sum_bi_glm <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), model_type = 'glm', family = 'binomial') #note that these are log-transformed
png("simpleEffPlot.png")
plot_coef_sum(coef_sum_bi_glm)
dev.off()
```

```{r}
#coef_sum_mv_glm <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), other_covariates = c("log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"), model_type = 'glm')
#plot_coef_sum(coef_sum_mv_glm)
coef_sum_mv_glm <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), other_covariates = c("log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"), model_type = 'glm', topics=c("Topic7", "Topic18", "Topic20", "Topic25", "Topic34"))
png("linearWithCtrl.png")
plot_coef_sum(coef_sum_mv_glm)
dev.off()
```


```{r}
#coef_sum_mv_hlm <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), other_covariates = c("log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"), grouping_var = 'GEOID10', model_type = 'lmer')
#plot_coef_sum(coef_sum_mv_hlm)
coef_sum_mv_hlm_five <- estimate_effects(data, focal_covariates = c("black_proportion", "asian_proportion", "latinx_proportion"), other_covariates = c("log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"), grouping_var = 'GEOID10', model_type = 'lmer', topics=c("Topic7", "Topic18", "Topic20", "Topic25", "Topic34"))
plot_coef_sum(coef_sum_mv_hlm_five)
#uses transformed race and topic data

```


```{r}
#doesn't work
#model_list <- estimate_effects(data, topics = c('Topic7', 'Topic18','Topic20','Topic25','Topic34'), focal_covariates = c("white_proportion"), other_covariates = c("log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"), grouping_var = 'GEOID10', model_type = 'lmer', return_model = TRUE, control =  lmerControl('bobyqa'))
#plot_coef_sum(coef_sum_more)

```

```{r}
library(texreg)
m0 <- lmer(Topic20 ~ white_proportion + (1|GEOID10),  data = data)
m1 <- lmer(Topic20 ~ white_proportion + log_price + log_sqft + log_income + pov_proportion + pop_thousands + share_oo + share_rental_over_20 + share_built_after_10 + share_commuters + share_college + (1|GEOID10),  data = data)
m2 <- lmer(Topic20 ~ white_proportion + log_price + log_sqft + log_income + pov_proportion + pop_thousands + share_oo + share_rental_over_20 + share_built_after_10 + share_commuters + share_college + (1 + white_proportion |GEOID10),  data = data)
m3 <- lmer(Topic20 ~ white_proportion + log_price + log_sqft + log_income + pov_proportion + pop_thousands + share_oo + share_rental_over_20 + share_built_after_10 + share_commuters + share_college + (1 + pop_thousands |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = data)


screenreg(c(m0,m1, m2, m3))
ranef <- ranef(m3)

# commenting out because it returns null
#plot(ranef$GEOID10$white_proportion)
plot(ranef$GEOID10, ranef$white_proportion)

dataT$dem_log_price <- data$log_price - mean(data$log_price)
dataT$dem_log_sqft <- data$log_sqft - mean(data$log_sqft)
dataT$dem_log_income <- data$log_income - mean(data$log_income)
dataT$dem_pov_proportion <- data$pov_proportion - mean(data$pov_proportion)
dataT$dem_pop_thousands <- data$pop_thousands - mean(data$pop_thousands)
dataT$dem_share_oo <- data$share_oo - mean(data$share_oo)
dataT$dem_share_rental_over_20 <- data$share_rental_over_20 - mean(data$share_rental_over_20)
dataT$dem_share_built_after_10 <- data$share_built_after_10 - mean(data$share_built_after_10)
dataT$dem_share_commuters <- data$share_commuters - mean(data$share_commuters)
dataT$dem_share_college <- data$share_college - mean(data$share_college)
dataT$dem_black_proportion <- dataT$black_proportion - mean(dataT$black_proportion) #logged version
dataT$dem_white_proportion <- dataT$white_proportion - mean(dataT$white_proportion) #logged version
dataT$dem_latinx_proportion <- dataT$latinx_proportion - mean(dataT$latinx_proportion) #logged version
dataT$dem_asian_proportion <- dataT$asian_proportion - mean(dataT$asian_proportion) #logged version

msimple_7 <- lm(Topic7 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion, data = dataT)
msimple_18 <- lm(Topic18 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion, data = dataT)
msimple_20 <- lm(Topic20 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion, data = dataT)
msimple_25 <- lm(Topic25 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion, data = dataT)
msimple_34 <- lm(Topic34 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion, data = dataT)

mlin_7 <- lm(Topic7 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college, data = dataT)
mlin_18 <- lm(Topic18 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college, data = dataT)
mlin_20 <- lm(Topic20 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college, data = dataT)
mlin_25 <- lm(Topic25 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college, data = dataT)
mlin_34 <- lm(Topic34 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college, data = dataT)

m3_7 <- lmer(Topic7 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college  + (1 |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = dataT)
m3_18 <- lmer(Topic18 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college  + (1 |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = dataT)
m3_20 <- lmer(Topic20 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college  + (1  |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = dataT)
m3_25 <- lmer(Topic25 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college  + (1 |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = dataT)
m3_34 <- lmer(Topic34 ~ dem_black_proportion + dem_asian_proportion + dem_latinx_proportion + dem_log_price + dem_log_sqft + dem_log_income + dem_pov_proportion + dem_pop_thousands + dem_share_oo + dem_share_rental_over_20 + dem_share_built_after_10 + dem_share_commuters + dem_share_college  + (1 |GEOID10), lmerControl(optimizer = 'bobyqa'), REML = FALSE,  data = dataT)

BIC(mlin_7) - BIC(m3_7)
BIC(mlin_18)- BIC(m3_18)
BIC(mlin_20) - BIC(m3_20)
BIC(mlin_25) - BIC(m3_25)
BIC(mlin_34) - BIC(m3_34)

bic.min <- function(var){
  model <- lmer(paste("Topic20 ~ white_proportion + log_price + log_sqft + log_income + pov_proportion + pop_thousands + share_oo + share_rental_over_20 + share_built_after_10 + share_commuters + share_college + (1 +",var,"|GEOID10)"), lmerControl(optimizer = 'bobyqa'), REML = FALSE, data = dataT)
  return(model)
}
vars <- c("white_proportion", "log_price", "log_sqft", "log_income", "pov_proportion", "pop_thousands", "share_oo", "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college")
#complains about singular fits and failures to converge
models <- map(vars, bic.min)
screenreg(models)
#20, 7, 25, 18, 34
```


## Let's do some Model Comparison using BIC

Using imageplot.bma to confirm our choice of covariates.
  
For Topic 7: Vintage Charm   
```{r}
library(BMA)
X <- dataT %>% select("black_proportion","asian_proportion", "latinx_proportion", "log_price", "log_sqft", "log_income", "pov_proportion", "pop_thousands", starts_with("share"), lat, lng)


bic.glm.07<- bic.glm(as.matrix(X), as.matrix(data %>% select(Topic7)), glm.family=gaussian)
png("model7_colorblock.png")
imageplot.bma(bic.glm.07)
dev.off()
```
    
Sound and City Views (18)  
  
```{r}
bic.glm.18<- bic.glm(as.matrix(X), as.matrix(dataT %>% select(Topic18)), glm.family=gaussian)
png("model18_colorblock.png")
imageplot.bma(bic.glm.18)
dev.off()
```
  
Developments as Communities (20)
  
```{r}
bic.glm.20<- bic.glm(as.matrix(X), as.matrix(dataT %>% select(Topic20)), glm.family=gaussian)
png("model20_colorblock.png")
imageplot.bma(bic.glm.20)
dev.off()
```
  
Top School Districts (25)  
  

```{r}
bic.glm.25<- bic.glm(as.matrix(X), as.matrix(dataT %>% select(Topic25)), glm.family=gaussian)
png("model25_colorblock.png")
imageplot.bma(bic.glm.25)
dev.off()
```
  
Embedded in Neighborhoods (34)  
  
```{r}
bic.glm.34<- bic.glm(as.matrix(X), as.matrix(dataT %>% select(Topic34)), glm.family=gaussian)
png("model34_colorblock.png")
imageplot.bma(bic.glm.34)
dev.off()
```

```{r}
# produce demeaned versions and logged versions of covariates of interest
#"log_price", "log_sqft"   ,          "log_income",        "pov_proportion" ,     "pop_thousands","share_oo" ,            "share_rental_over_20", "share_built_after_10", "share_commuters", "share_college"

data$dem_log_price <- data$log_price - mean(data$log_price)
data$dem_log_sqft <- data$log_sqft - mean(data$log_sqft)
data$dem_log_income <- data$log_income - mean(data$log_income)
data$dem_pov_proportion <- data$pov_proportion - mean(data$pov_proportion)
data$dem_pop_thousands <- data$pop_thousands - mean(data$pop_thousands)
data$dem_share_oo <- data$share_oo - mean(data$share_oo)
data$dem_share_rental_over_20 <- data$share_rental_over_20 - mean(data$share_rental_over_20)
data$dem_share_built_after_10 <- data$share_built_after_10 - mean(data$share_built_after_10)
data$dem_share_commuters <- data$share_commuters - mean(data$share_commuters)
data$dem_share_college <- data$share_college - mean(data$share_college)


```